### 2021-03-21 docs/submission/srep/coverletter/letter-tex/covlet.tex
#6 polishes cover letter

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------
\begin{flushright}
\large\bf Miguel Xochicale \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
4th Floor \\
Lambeth Wing  St. Thomas' Hospital \\
Westminster Bridge Road \\
London SE1 7EH \\
\faEnvelopeO  miguel.xochicale@kcl.ac.uk \\
\faMobile  (+44) 0744 281 7616 \\
\faHome \href{http://mxochicale.github.io}{http://mxochicale.github.io}
%\vspace{20pt}
%\large\bf Chris Baber, Professor \\ % Your name
%%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
%123 Broadway \\ City, State 12345 \\ (000) 111-1111 % Your address and phone number
\end{flushright}

@@

%* A brief explanation of why the work is appropriate for Scientific Reports
Our work is appropriate for Scientific Reports due to its alignment to the principles of open science (e.g., reproducibility, transparency, reusability and open accessibility).   
Similarly, we choose Scientific Reports because of the potential reachability to readers in areas of natural and clinical sciences along with potential application of our work and the spark for collaborations.

@@

%* The names and contact information of any reviewers you consider suitable
%* The names of any referees you would like excluded from reviewing
Finally, two potential reviewers for our work can be: Bedartha Goswami, bedartha.goswami@uni-tuebingen.de, at University of Tübingen investigating nonlinear time series analysis; recurrence plots, and Serhiy Yanchuk, yanchuk@math.tu-berlin.de, at Technical University of Berlin investigating dynamics time delay networks of dynamical systems; pattern formation; coupled systems.

@@

\encl{manuscript and supplementary document} 
% List your enclosed documents here, comment this out to get rid of the "encl:"
%----------------------------------------------------------------------------------------

>>>>

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------
\begin{flushright}
\large\bf Miguel Xochicale \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
%School of Electronic, Electrical and Systems Engineering\\
Edgbaston\\
Birmingham\\
B15 2TT\\
UK\\
\faEnvelopeO  perez.xochicale@gmail.com \\
\faMobile  (+44) 0744 281 7616 \\
\faHome \href{http://mxochicale.github.io}{http://mxochicale.github.io}
%\vspace{20pt}
%\large\bf Chris Baber, Professor \\ % Your name
%%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
%123 Broadway \\ City, State 12345 \\ (000) 111-1111 % Your address and phone number
\end{flushright}

@@

%* A brief explanation of why the work is appropriate for Scientific Reports
Our work is appropriate for Scientific Reports due to its alignment to the principles of open science (e.g., reproducibility, transparency, reusability and open accessibility).   
Similarly, we choose Scientific Reports as venue where potential interest of readers in areas of natural and clinical sciences along with potential application of our work and the spark for collaborations.

@@

%* The names and contact information of any reviewers you consider suitable
%* The names of any referees you would like excluded from reviewing
Finally, two suitable reviewers for our work would be: Bedartha Goswami, bedartha.goswami@uni-tuebingen.de, at University of Tübingen, for his investigation in nonlinear time series analysis and recurrence plots; and Serhiy Yanchuk, yanchuk@math.tu-berlin.de, at Technical University of Berlin, for his research in dynamics time delay networks of dynamical systems, pattern formation, and coupled systems.

@@

\encl{Manuscript and supplementary document} 
% List your enclosed documents here, comment this out to get rid of the "encl:"
%----------------------------------------------------------------------------------------
